Carrying out Latent Profile Analysis in Accordance With Best Practices: A Tutorial Using the tidyLPA R package

### 2020-08-26 paper.rmd
update

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
library(tidyverse)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = TRUE)
```

@@

``` {r, curry-mac-mclust}
m1 <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(1:10)
```

@@

```{r}
get_fit(m1)
```

@@

We can use Mplus simply by changing the package argument for
`estimate_profiles()` to "mplus" or "MplusAutomation" (either will work):

@@

``` {r, compare-mclust, eval = FALSE}
curry_mac_mclust_solutions <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9) %>%
  compare_solutions(statistics = c("AIC", "BIC"))

write_rds(curry_mac_mclust_solutions, "cm_mclust.rds")

# Best model according to AIC is Model 6 with 7 classes.
# Best model according to BIC is Model 6 with 2 classes.

#An analytic hierarchy process, based on the fit indices AIC, AWE, BIC, CLC, and KIC (Akogul & Erisoglu, 2017), suggests the best solution is Model 6 with 2 classes.
```

````{r, just-one}
urry_mac %>% 
  select(KinshipR:PossessionR) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9)

curry_mac_mclust_j <- curry_mac %>% 
  select(KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9)

curry_mac_mclust_j <- curry_mac %>% 
  select(KinshipR:PossessionR) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9,
                    package = "mplus")

curry_mac %>% 
  select(KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9,
                    package = "mplus")
```

@@

```{r, m6p7-solution, eval = FALSE}
curry_mac_m6p7 <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(3, 
                    variances = "varying",
                    covariances = "varying")

plot_profiles(curry_mac_m6p7)
```

```{r, m6p2-solution, eval = FALSE}
curry_mac_m6p2 <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(3, 
                    variances = "varying",
                    covariances = "varying")

plot_profiles(curry_mac_m6p7)
```

We can also run the same process using mplus:

``` {r, compare-mplus, eval = FALSE}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9, package = "mplus") %>%
  compare_solutions(statistics = c("AIC", "BIC"))
```

```{r, m6ps-mplus, eval = FALSE}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(n_profiles = 2, 
                    variances = "varying",
                    covariances = "varying", 
                    package = "mplus")

```

```{r, m6p2-mclust, eval = FALSE}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(n_profiles = 2, 
                    variances = "varying",
                    covariances = "varying")

```

@@

``` {r}
get_data()
```

@@

``` {r}
get_data(m) %>% 
  tidyr::gather(Class_prob, Probability, contains("CPROB"))
```

>>>>

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
library(tidyverse)
knitr::clean_cache()
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

@@

``` {r, curry-mac-mclust-example}
m1 <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(1:10)
```

@@

```{r, get-fit-m1}
get_fit(m1)
```

@@

We can use Mplus simply by changing the package argument for
`estimate_profiles()` to "mplus" or "MplusAutomation" (either will work; not run here):

@@

````{r, compare-mclust}
compare_solutions_mclust <- curry_mac %>% 
  select(KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9,
                    package = "mclust")
```

```{r, eval = FALSE}
write_rds(compare_solutions_mclust, "compare_solutions_mclust.rds")
````

```{r, compare-mplus}
compare_solutions_mplus <- curry_mac %>% 
  select(KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 4, 5, 6),
                    n_profiles = 1:9,
                    package = "mplus")
```

```{r, echo = FALSE}
write_rds(compare_solutions_mplus, "compare_solutions_mplus.rds")
```

```{r, compare-mplus-starts}
compare_solutions_mplus_starts <- curry_mac %>% 
  select(KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 4, 5, 6),
                    n_profiles = 1:9,
                    package = "mplus",
                    ANALYSIS = "starts = 100, 20;")
```

```{r, echo = FALSE}
write_rds(compare_solutions_mplus_starts, "compare_solutions_mplus_starts.rds")
```

@@

@@

``` {r, eval = FALSE}
get_data()
```

@@

``` {r, eval = FALSE}
get_data(m) %>% 
  tidyr::gather(Class_prob, Probability, contains("CPROB"))
```
